---
title: ""
output:
  pdf_document: default
  html_document:
    keep_md: TRUE
    highlight: pygments
    theme: cerulean
  word_document: default
---

----

**Code for Model**  

----

```{R}
library(dplyr)
library(ggplot2)
library(ggfortify)
library(GGally)
library(Hmisc)
library(glmnet)
library(pROC)
library(MLmetrics)
library(mice)
library(BBmisc)
library(gam)
# library(naniar)
library(mgcv)
library(plyr)

library(purrr, warn.conflicts = FALSE, quietly=TRUE)
library(tidyr, warn.conflicts = FALSE, quietly=TRUE)
library(cowplot, warn.conflicts = FALSE, quietly=TRUE)
library(corrplot, warn.conflicts = FALSE, quietly=TRUE)
library(pander, warn.conflicts = FALSE, quietly=TRUE)
library(DAAG, warn.conflicts = FALSE, quietly=TRUE)
library(lmtest, warn.conflicts = FALSE, quietly=TRUE)
```



# load data
```{R}
killing <- read.csv("police_killings_cleaned.csv")
survey <- read.csv("acs2015_census_tract_data.csv")
# killing$share_black <- as.numeric(as.character(killing$share_black))
```

```{R}
# get column names
colnames(killing)   
#sapply(killing, class)
```
# Hypothesis testing    
## Aggregate data   
Calculate the difference between proportion of African American given killed and the proportion of African American in each state   
```{r}
killarst = killing[c("raceethnicity","state", "geo_id","pop","share_black")]
killarst$isblack = killarst$raceethnicity =="Black"
killarst$state=as.character(killarst$state)
df1 = count(killarst, c('isblack','state'))
df1 = df1[df1$isblack==TRUE, ]
df2 = count(killarst, c('state'))
df3 = merge(x = df1, y = df2, by = "state", all.y = TRUE)
df3$freq.x[is.na(df3$freq.x)] <- 0
df3$killprob = df3$freq.x/df3$freq.y
df3 = df3[c("state","freq.x","freq.y","killprob")]
statename = data.frame(state.name, state.abb)
statename$state.name = as.character(statename$state.name)
statename$state.abb = as.character(statename$state.abb)
statename = statename %>% add_row(state.name = "Puerto Rico", state.abb = "PR") %>% 
  add_row(state.name = "District of Columbia", state.abb = "DC")
dfs1 = survey[c("State", "TotalPop","Black")]
dfs1 = dfs1[complete.cases(dfs1),]
dfs1$State = as.character(dfs1$State)
dfs1$blackpop = dfs1$TotalPop*dfs1$Black/100
dfs1 = aggregate(dfs1[c("TotalPop","blackpop")], by=list(State=dfs1$State), FUN=sum)
dfs1$b_prop = dfs1$blackpop/dfs1$TotalPop   
dfs1 = merge(x=dfs1, y = statename, by.x="State", by.y="state.name",all.x = TRUE)
```

```{r}
d_test = merge(x=df3, y=dfs1, by.x = "state", by.y = "state.abb", all.x = TRUE)
```

```{r}
d_test$probdiff = d_test$killprob-d_test$b_prop
```

There are a few states with *probdiff* < 0, but that is likely due to lack of data (those states only have a few instances)
```{r}
d_test
```
Run t-test, the p value and confidence interval indicates that the difference between proportion of African American given killed and the proportion of African American in each state are likely to be positive. 
```{r}
t.test(d_test$probdiff)
```

# Model 1, Poisson regression   
Load data 
```{r}
dfmega = merge(x = killing, y = survey, by.x = "geo_id", by.y = "CensusTract", all.x=TRUE)
dfmega = dfmega %>% select(c("geo_id", "County", "pop", "share_white", "share_black", "share_hispanic", "pov", "college", "Men", "Citizen", "IncomePerCap", "ChildPoverty", "Unemployment","Professional","Service","Drive","Transit","TotalPop"))
```
Remove empty value because there are only a few of them   
```{r}
nrow(dfmega[!complete.cases(dfmega),])
```

```{r}
dfmega = dfmega[complete.cases(dfmega),]
```

Change a few datatypes   
```{r}
dfmega$share_black = as.numeric(as.character(dfmega$share_black))
# dfmega$share_black = dfmega$share_black*dfmega$pop/100
dfmega$share_white = as.numeric(as.character(dfmega$share_white))
# dfmega$share_white = dfmega$share_white*dfmega$pop/100
dfmega$share_hispanic = as.numeric(as.character(dfmega$share_hispanic))
# dfmega$share_hispanic = dfmega$share_hispanic*dfmega$pop/100
dfmega$pov = as.numeric(as.character(dfmega$pov))
dfmega$Men = dfmega$Men/dfmega$TotalPop*100
dfmega$Citizen = dfmega$Citizen/dfmega$TotalPop*100
dfmega$college = dfmega$college*100
# dfmega$pov = dfmega$pov*dfmega$pop/100
```

```{r}
colnames(dfmega)
```

Calculate county level statistics   
```{r}
col = c("share_white", "share_black", "share_hispanic", "pov", "college", "Men", "Citizen", "ChildPoverty", "Professional","Service","Drive","Transit", "Unemployment")
```

```{r}
for (i in 1:13) {
  dfmega[col[i]] = dfmega[col[i]]*dfmega$pop
}
dfmega$IncomePerCap = dfmega$IncomePerCap*dfmega$pop
```

```{r}
dfmega = as.data.frame(append(dfmega, 1.0)) 
colnames(dfmega)[19] = "count"
```

```{r}
dfcounty = aggregate(dfmega[c("pop", "IncomePerCap", col, "count")], by=list(county=dfmega$County), FUN=sum)
```

```{r}
for (i in 1:13) {
  dfcounty[col[i]] = dfcounty[col[i]]/dfcounty$pop/100
}
dfcounty$IncomePerCap = dfcounty$IncomePerCap/dfcounty$pop
```

```{r}
dfcounty$IncomePerCap = normalize(dfcounty$IncomePerCap, method = "range", range = c(0, 1))
dfcounty$pop = normalize(dfcounty$pop, method = "range", range = c(0, 1))
```

```{r}
dfcounty
```

Converte data to matrix  
```{r}
Xv = model.matrix(count~.-county, dfcounty)[,-1]
yv = dfcounty$count
grid = 10^seq(3, -10, length = 500)
```

```{r}
hist(dfcounty$count)
```

```{r}
plot(glmnet(Xv, yv, alpha=1, lambda = grid, family = "poisson"),xvar="lambda")   
```

Run poisson regression with L1 regulization, cross validation to find penalty weight   
```{r}
cvfitlasso = cv.glmnet(Xv, yv, alpha=1, lambda = grid, family = "poisson", type.measure = "deviance")
```

```{r}
plot(cvfitlasso)
```
cv result of penalty weight   
```{r}
cvfitlasso$lambda.min
```
result of the model  
```{r}
coef(cvfitlasso)
```

```{r}
glmnet(Xv, yv, alpha=1, lambda = cvfitlasso$lambda.min, family = "poisson")
```

According to the result, basically, no other features explains how many people got killed in the county except the population. 

# Model 2, logistic regression   
Load data  
```{r}
df1_1 = killing[c('age','gender','raceethnicity','month','year','city','state','geo_id','cause','armed','pop','share_black','p_income','h_income','county_income','county_bucket', 'nat_bucket','pov', 'urate', 'college')]
df2_1 = survey[,!names(survey) %in% c('State','Unemployment')]

```

```{r}
dfall = merge(x = df1_1, y = df2_1, by.x = "geo_id", by.y = "CensusTract", all.x=TRUE)
```

```{r}
colSums(is.na(dfall))
```
Remove empty values because there are only a few of them   
```{r}
nrow(dfall[!complete.cases(dfall),])
```

```{r}
dfall = dfall[complete.cases(dfall),]
```
Convert a few variables  
```{r}
dfall$share_black = as.numeric(as.character(dfall$share_black))
dfall$p_income = as.numeric(as.character(dfall$p_income))
dfall$pov = as.numeric(as.character(dfall$pov))
dfall$county_bucket = as.factor(dfall$county_bucket)
dfall$nat_bucket = as.factor(dfall$nat_bucket)
```

```{r}
dfall$isblack = dfall$raceethnicity == "Black"  
dfall$isblack = as.factor(dfall$isblack)
```

```{r}
dfall$citizenrate = dfall$Citizen/dfall$TotalPop
dfall$menrate = dfall$Men/dfall$TotalPop
dfall$womenrate = dfall$Women/dfall$TotalPop   
```

```{r}
dfall$isarmed = dfall$armed!="No"
```

The following function calculates the AUC   
```{r}
getauc <- function (model) {
  tempp = predict(model, dfall, type="response")
  roc = pROC::roc(dfall$isblack, tempp)
  pROC::auc(roc)
}

```

Fit a model with forward selection using AIC   
```{r, include=FALSE}
glm.null = glm(isblack~1,data=dfall, family="binomial")
glm.full = glm(isblack~.-geo_id-raceethnicity-year-cause-city-state-County-TotalPop-armed-Citizen-Men-Women, data = dfall, family="binomial")  
forward.glm = step(glm.null,scope=list(lower=glm.null,upper=glm.full), direction="forward", k = 2)
```

In the full model, some variables has high VIF. It is reasonable to see this because for example, poverty rate should be somewhat related to the county's median income. Moreover, a richer area is likely to have higher education rate.   
```{r}
vif(glm.full)
```

Result of forward selection:  

```{r, echo = FALSE}
panderOptions('table.continues', '')
set.alignment('left', row.names = 'right')
pander(summary(forward.glm), type = 'grid', style = "simple", add.significance.stars = TRUE, split.table = 200)
```
Pacific and OtherTransp are not significant. I then tried to remove these two variables and built a reduced model   
```{r}
glmreduced = glm(isblack~share_black+county_income+age+pop+Carpool+SelfEmployed+Office+isarmed, data = dfall, family="binomial")
```

```{r}
getauc(glmreduced)
```
According to the LR test, there is no significant envidence to show that the forward selection model is better than the reduced model 
```{r}
lrtest(forward.glm, glmreduced)   
```


We tried to add few interaction terms such as isarmed*age. But after doing a LR test, there is no significant envidence to show that adding the interaction will make the model better. So we did not ended up with any interaction terms.  
```{r}
glm_int = glm(isblack~share_black+county_income+age+pop+Carpool+SelfEmployed+Office+isarmed+isarmed*age, data = dfall, family="binomial")
lrtest(glm_int, glmreduced)
```

Therefore, we choose the reduced model   
```{r}
pander(summary(glmreduced), type = 'grid', style = "simple", add.significance.stars = TRUE, split.table = 200)
```


Checking the Residual and Leverage of the model, there are a few high leverage points and high residual points. But there is not point with high cook's distance, which means there are no influencial outliers.    
```{r}
plot(glmreduced, which =5)
```

We checked the caliberation. I sorted the data by prediction probability and break them into 10 groups. Within each group, I checked the average predicted probability and the percentage of African Americans. They look fairly similar. Therefore, the model seem to be well calibrated.    
```{r}
pred = predict(glmreduced, dfall, type="response")   
```

```{r, echo=FALSE}
ordering = order(pred)
avg.probs = numeric(10)
avg.kill = numeric(10)
for (i in 1:10){
  start = (i-1)*47+1
  end = min(467,start+47)
  avg.probs[i] = mean(pred[ordering[start:end]])
  avg.kill[i] = mean(dfall$isblack[ordering[start:end]] == TRUE)
}
ggplot()+geom_point(aes(x=avg.probs,y=avg.kill))+geom_abline(aes(slope=1,intercept=0),col="red")
```
